### 2017-03-22 main.tex
Really final data for Table~\ref{table:accuracies}! Still need to update the figure.
Update version link to Nathan's Swift code.

\begin{table}
  % replot_accuracies_concatanated('tex', true) for confusion_log_perf.txt (1.5 ms).
  \begin{tabular}{lc|cc}
    Bird & Target time (ms) & \% True positives & \% False positives \\ \hline
lny64 &         150 $[t^*_1]$ &         99.66 &         0.0026 \\ % /Volumes/Data/song/lny64/confusion_log_perf.txt
      &         200 $[t^*_2]$ &         99.75 &         0.00052 \\ %                                               
      &         250 $[t^*_3]$ &         99.79 &         0.00051 \\ %                                               
      &         300 $[t^*_4]$ &         99.70 &         0.00077 \\ %                                               
      &         350 $[t^*_5]$ &         99.73 &         0.00022 \\ %                                               
      &         400 $[t^*_6]$ &         99.52 &         0.0010 \\ %                                                
lny42 &         380 &   99.09 &         0.0011 \\ % /Volumes/Data/song/lny42/confusion_log_perf.txt          
lny46 &         140 &   99.17 &         0.0037 \\ % /Volumes/Data/song/lny46/confusion_log_perf.txt          
lny4rb &        250 &   99.37 &         0.0026 \\ % /Volumes/Data/song/lny4rb/confusion_log_perf.txt        
lr12 &  180 &   99.52 &         0.0033 \\ % /Volumes/Data/song/lr12/all/confusion_log_perf.txt        
lr13 &  300 &   99.83 &         0.0013 \\ % /Volumes/Data/song/lr13/all/confusion_log_perf.txt        
lr28 &  140 &   99.73 &         0.0028 \\ % /Volumes/Data/song/lr28/all/confusion_log_perf.txt        
lr77 &  320 &   99.58 &         0.0028  % /Volumes/Data/song/lr77/all/confusion_log_perf.txt          
  \end{tabular}
  \caption{Mean values for the detection accuracies shown in \fig{fig:accuracies}.}
  \label{table:accuracies}
\end{table}

@@

  \item[Swift:] {\tt https://github.com/gardner-lab/\dots\ syllable-detector-swift/releases/tag/0.3.1}

>>>>

\begin{table}
  % replot_accuracies_concatanated('tex', true) for confusion_log_perf.txt (1.5 ms).
  \begin{tabular}{lc|cc}
    Bird & Target time (ms) & \% True positives & \% False positives \\ \hline
lny64 &         150 $[t^*_1]$ &         99.66 &         0.0026 \\ % /Volumes/Data/song/lny64/confusion_log_perf.txt
      &         200 $[t^*_2]$ &         99.75 &         0.00052 \\ %                                               
      &         250 $[t^*_3]$ &         99.79 &         0.00051 \\ %                                               
      &         300 $[t^*_4]$ &         99.70 &         0.00077 \\ %                                               
      &         350 $[t^*_5]$ &         99.73 &         0.00022 \\ %                                               
      &         400 $[t^*_6]$ &         99.52 &         0.0010 \\ %                                                
lny42 &         380 &   99.09 &         0.0011 \\ % /Volumes/Data/song/lny42/confusion_log_perf.txt          
lny46 &         140 &   99.11 &         0.0036 \\ % /Volumes/Data/song/lny46/confusion_log_perf.txt          
lny4rb &        250 &   99.37 &         0.0026 \\ % /Volumes/Data/song/lny4rb/confusion_log_perf.txt        
lr12 &  180 &   99.52 &         0.0033 \\ % /Volumes/Data/song/lr12/all/confusion_log_perf.txt        
lr13 &  300 &   99.83 &         0.0013 \\ % /Volumes/Data/song/lr13/all/confusion_log_perf.txt        
lr28 &  140 &   99.73 &         0.0028 \\ % /Volumes/Data/song/lr28/all/confusion_log_perf.txt        
lr77 &  320 &   99.58 &         0.0028  % /Volumes/Data/song/lr77/all/confusion_log_perf.txt          
  \end{tabular}
  \caption{Mean values for the detection accuracies shown in \fig{fig:accuracies}.}
  \label{table:accuracies}
\end{table}

@@

  \item[Swift:] {\tt https://github.com/gardner-lab/\dots\ syllable-detector-swift/releases/tag/0.3.2}
